Comparing MTurk and the US Population's Occupational Diversity

### 2018-09-17 Manuscript.Rmd
Replication Demographic Analysis

>>>>

###Replication Demographic Analaysis
#Age Analysis T- Test
#Load Dataset
require(dplyr)
require(readxl)
BLS_age <- read_excel("age_demo.xlsx")

#Define population mean. In this case it was already calculated in the dataset. 
pop_mean <- as.numeric(age_demo[6 , 10])

#Define sample mean
MTurk17 <- read_excel("~/MTurk Diversity 2017 Data/2017 Data.xls")
samp_mean <- as.numeric(MTurk17 %>%
  summarise(MTurk_age = mean(What.is.your.age., na.rm = TRUE)))

#Not able to get population standard deviation. Estimated using sample standard deviation.
samp_sd <- as.numeric(MTurk17 %>%
  summarise(sd_age = sd(What.is.your.age., na.rm = TRUE)))

#Define sample size
n <- as.numeric(667)

#Run t test.
t_value <- (samp_mean - pop_mean)/(samp_sd/sqrt(n))
View(t_value)

##Gender Analysis
BLS_data <- read_excel("employment_demo.xlsx")

#Get BLS gender data (expected value)
BLS_women <- as.numeric(BLS_data[7,3])/100
BLS_men <- 1.000 - BLS_women

BLS_gender <- c(BLS_women, BLS_men, 0.0)

#Get MTurk gender data (observed value)
MTurk_gender <- MTurk17 %>%
  count(What.is.your.gender.)

#Define confidence intervals
require(binom)
gCI <- binom.confint(x = MTurk_gender$n, n = sum(MTurk_gender$n), conf.level = 0.95, methods = "exact")
gCI <- gCI[ , 4:6]

#Build Gender table with gender, expected value, n, LL, observed, UL
gender_table <- cbind(MTurk_gender, gCI, BLS_gender)
names(gender_table) <- c("gender", "n", "o", "LL_g", "UL_g", "e")
gender_table <- gender_table[ 1, c(1, 2, 3, 4, 6, 5)]
View(gender_table)

#Gender chi square test

chi2 <- function(x) {
  o <- (x$n)
  e <- (x$e)
  n <- sum(x$n, na.rm=TRUE)
  ((o-(e)*(n))^2)/((e)*(n))
}

gender_ch2 <- as.data.frame(chi2(gender_table))
names(gender_ch2) <- c("chi2")
row.names(gender_ch2) <- c("female")
gender_ch2 <- na.omit(gender_ch2)
View(gender_ch2)

#Sum chi-square values.
sum(gender_ch2$chi2, na.rm=TRUE)

#Ethnicity Analysis 
#Define obs_eth
BLS_cauc <- as.numeric(BLS_data[7, 4])/100
BLS_AfAm <- as.numeric(BLS_data[7,5])/100
BLS_Asn <- as.numeric(BLS_data[7,6])/100
BLS_Hisp <- as.numeric(BLS_data[7,7])/100
BLS_eth <- c(BLS_AfAm, BLS_Asn, BLS_cauc, BLS_Hisp)

sum(BLS_eth)

#Get MTurk ethnicity data
MTurk_eth <- MTurk17 %>%
  count(MTurk17$With.which.ethnicity.do.you.most.identify.)

#Define confidence intervals 
ethCI <- binom.confint(x = MTurk_eth$n, n = sum(MTurk_eth$n), conf.level = 0/95, methods = "exact")
ethCI <- ethCI[ , 4:6]

#Build Ethnicity table 
ethnicity_table <- cbind(MTurk_eth, ethCI, BLS_eth)
names(ethnicity_table) <- c("ethnicity", "n", "o", "LL_eth", "UL_eth", "e")
eth_table <- ethnicity_table[1:4 , c(1, 6, 2, 4, 3, 5)]
View(eth_table)

#Ethnicity chi squared test
eth_ch2 <- as.data.frame(chi2(eth_table))
names(eth_ch2) <- c("chi2")
row.names(eth_ch2) <- c("African American", "Asian", "Caucasian", "Hispanic")
eth_ch2 <- na.omit(eth_ch2)
View(eth_ch2)

#Sum chi-square values.
sum(eth_ch2$chi2, na.rm=TRUE)
